---
title: "markdown_test"
output: html_document
date: "2024-01-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning=FALSE)
```

```{r}
pacman::p_load(tidyverse, haven, jtools, lme4, lmerTest, lfe, sjPlot)
rm(list = ls())
```

## Cross-sectional anti-immigration modelling

Dependent variable and model:  

* Opposition to immigration measured on an 11-point scale from 0 (should allow many more immigrants) to 10 (should allow far fewer immigrants)  
* Nested multilevel linear model with random intercepts for local authorities, with cross-level interactions between housing affordability and a) social renting and b) homeownership  
* Affordability measured via the ratio of median house prices to median earnings in a local authority; as such, a higher number indicates more unaffordable housing  

Key findings:  

* The association between affordability and opposition to immigration is conditional on tenure
* A positive interaction exists between social renting and unaffordability  
* A negative interaction exists between homeownership and unaffordability   
* Findings robust to log transformation of affordability, using log of house prices as independent variable, and inclusion of regional dummies  

```{r, include=TRUE}
# plot
readRDS("working/markdown_viz/immi_coefs.RDS")
```

The figure below displays the interaction terms. It also shows that once controlling for the confounding influence of the percentage of people with degrees in a local authority, for many tenures there is a positive association between high house prices and right wing political attitudes.  

```{r, include = TRUE}
readRDS("working/markdown_viz/int_plot.RDS")
```

## Cross-sectional immigrants a burden on welfare modelling

Dependent variable and model:  

* Binary indicator for whether respondents 'agree' or 'strongly agree' that immigrants are a burden on the welfare state    
* Nested multilevel logit model with random intercepts for local authorities, with cross-level interactions between housing affordability and a) social renting and b) homeownership  

Key findings:  

* Positive association with social renting and homeownership  
* Positive interaction between social renting and affordability i.e. social renters in less affordable areas more likely to see immigrants as a welfare state burden  
* Interaction between social renting and affordability robust to using log of affordability, log of house prices, and inclusion of regional dummies  
* No interaction with homeownership  

```{r, include=TRUE}
# plot
readRDS("working/markdown_viz/immi_burden_coefs.RDS")
```

## Cross-sectional racial equality modelling

Dependent variable and model:  

* Opposition to racial equality measured as a binary indicator (1 = racial equality has "gone too far" or "gone too much far")  
* Nested multilevel logit model with random intercepts for local authorities, with cross-level interactions between housing affordability and a) social renting and b) homeownership  

Key findings:  

* No effect of housing affordability, or the interaction terms
* Homeowners more likely to think racial equality has gone too far than other tenures  

```{r, include=TRUE}
readRDS("working/markdown_viz/equality_coefs.RDS")
```

## Table of cross-sectional modelling results

```{r, include=TRUE, results = 'asis'}
immi_int <- readRDS("working/markdown_data/immi_tab.RDS")
equal_int <- readRDS("working/markdown_data/equal_int.RDS")
immi_bur <- readRDS("working/markdown_data/immig_burden_int.RDS")

tab_model(immi_int, immi_bur, equal_int, p.style = "stars", show.aic = T, 
          terms = c("social_housing", "homeowner", 
                    "private_renting", "affordability", 
                    "social_housing.affordability", 
                    "homeowner.affordability"),
          pred.labels = c("Social renter", "Homeowner", "Private renter",
                          "Affordability",
                          "Social renter * Affordability", 
                          "Homeowner * Affordability"),
          dv.labels = c("Anti-immigration", "Immigrants a welfare burden",  "Anti-racial equality"))
```


## Longitudinal anti-immigration modelling

Data and modelling strategy:

* Six waves of the British Election Study (BES) ranging from 2016-2021, filtered to respondents who participated in at least three waves  
* Random effect within-between (REWB) model with two-way cross-classified structure i.e. random intercept for respondent and random intercept for local authority  
* Cross-level interaction between between authority affordability and tenure (i.e. social renting and homeonwership, respectively)  

Key findings:  

* Association of between affordability with opposition to immmigration is again contingent upon tenure, with the direction of the interactions consistent with the cross-sectional modelling  
* Variation in affordability within local authorities also associated with the outcome variable; declining affordability within a local authority associated with more opposition to immigration  
* Findings robust to log scale of affordability, use of log house prices as independent variable, inclusion of change in the percentage of people degree educated between censuses as a control variable, and modelling of within local authority change via a fixed effects model  

```{r, include=TRUE, results = 'asis'}
immi_long <- readRDS("working/markdown_data/immi_int_long.RDS")

tab_model(immi_long, p.style = "stars", show.aic = T, 
          terms = c("social_housing", "homeowner", 
                    "private_renting", "affordability_mean",
                    "social_housing.affordability_mean",
                    "homeowner.affordability_mean",
                    "affordability_within"),
          pred.labels = c("Social renter", "Homeowner", "Private renter",
                          "Affordability between",
                          "Social renter * Affordability between",
                          "Homeowner * Affordability between",
                          "Affordability within"),
          dv.labels = c("Anti-immigration (longitudinal)"))
```

